---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# testthatmulti

<!-- badges: start -->
[![R-CMD-check](https://github.com/CollinErickson/testthatmulti/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CollinErickson/testthatmulti/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/CollinErickson/testthatmulti/branch/master/graph/badge.svg)](https://app.codecov.io/gh/CollinErickson/testthatmulti?branch=master)
[![Codecov test coverage](https://codecov.io/gh/CollinErickson/testthatmulti/graph/badge.svg)](https://app.codecov.io/gh/CollinErickson/testthatmulti)
<!-- badges: end -->

The goal of testthatmulti is to enhance the R package `testthat` so that noisy
tests can be run.
If a test fails 1% of the time, it can cause problems with R packages.
By allowing each test multiple attempts to pass, unexpected and rare test
failures can be avoided.

## Installation

You can install the development version of testthatmulti from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CollinErickson/testthatmulti")
```

## Example

For example, suppose you have a test that passes 99% of the time.
This can happen when tests are run using randomly generated data,
such as for modeling or optimization.

```{r example1, eval=T, error=T}
set.seed(153)
library(testthat)
x <- runif(1)
cat('x is', x, '\n')
expect_true(x < .99)
```

This test will usually pass, but could fail occasionally and cause
problems when submitting to CRAN.

To give the test multiple chances to pass, wrap the function
`ttm` around the code for the tests and tell it how many times to 
run the tests.
It will succeed if all the tests are passed on any single iteration.
In the code for the tests, replace `expect_true` with `ttm_expect_true`
and `expect_equal` with `ttm_expect_equal`.

Below, we run the same test as above, but give it 3 chances to pass.
By giving it 3 attempts to pass the test, the probability of failure
drops from 1% to 0.0001%

```{r example}
set.seed(153)
library(testthatmulti)
ttm(10, {
  x <- runif(1)
  cat('x is', x, '\n')
  ttm_expect_true(x < .99)
})
```
