---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# testthatmulti

<!-- badges: start -->
[![R-CMD-check](https://github.com/CollinErickson/testthatmulti/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CollinErickson/testthatmulti/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of testthatmulti is to enhance the R package `testthat` so that noisy
tests can be run.
If a test fails 1% of the time, it can cause problems with R packages.
By allowing each test multiple attempts to pass, unexpected and rare test
failures can be avoided.

## Installation

You can install the development version of testthatmulti from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("CollinErickson/testthatmulti")
```

## Example

For example, suppose you have a test that passes 99% of the time.
This can happen when tests are run using randomly generated data,
such as for modeling or optimization.

```{r example1, eval=F}
set.seed(153)
library(testthat)
x <- runif(1)
cat('x is', x, '\n')
expect_true(x < .99)
```

This test will usually pass, but could fail occasionally and cause
problems when submitting to CRAN.

To give the test multiple chances to pass, use the functions
`ttm` and `ttm_expect_true` from this package as follows.
By giving it 3 attempts to pass the test, the probability of failure
drops from 1% to 0.0001%

```{r example}
set.seed(153)
library(testthatmulti)
ttm(10, {
  x <- runif(1)
  cat('x is', x, '\n')
  ttm_expect_true(x < .99)
})
```

